US General Society Survey Analysis

### 2024-03-17 paper/paper.qmd

```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences
  ),
  statistic = "mad"
  )
```

# Results

>>>>

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of presidential election in 2020 based on gender and immigration status"
#| warning: false
modelsummary(
  list(
    "Support Biden" = political_preferences
  ),
  statistic = "mad"
  )
```
